\documentclass[letterpaper,10pt]{article}

\usepackage{graphicx}                                        
\usepackage{amssymb}                                         
\usepackage{amsmath}                                         
\usepackage{amsthm}                                          

\usepackage{alltt}                                           
\usepackage{float}
\usepackage{color}
\usepackage{url}

\usepackage{balance}
\usepackage[TABBOTCAP, tight]{subfigure}
\usepackage{enumitem}
\usepackage{pstricks, pst-node}

\usepackage{geometry}
\geometry{textheight=8.5in, textwidth=6in}

%random comment

\newcommand{\cred}[1]{{\color{red}#1}}
\newcommand{\cblue}[1]{{\color{blue}#1}}

\newcommand{\toc}{\tableofcontents}

%\usepackage{hyperref}

\def\name{Drake Bridgewater}

%pull in the necessary preamble matter for pygments output
%\input{pygments.tex}

%% The following metadata will show up in the PDF properties
% \hypersetup{
%   colorlinks = false,
%   urlcolor = black,
%   pdfauthor = {\name},
%   pdfkeywords = {cs411 ``operating systems 2''},
%   pdftitle = {CS 411 Project 1},
%   pdfsubject = {CS 311 Project 1},
%   pdfpagemode = UseNone
% }

\parindent = 0.0 in
\parskip = 0.1 in

\begin{document}

\tableofcontents

%input the pygmentized output of mt19937ar.c, using a (hopefully) unique name
%this file only exists at compile time. Feel free to change that.

\newpage

\section{What do you think the main point of this assignment is?} 
The purpose of this assignement is to give us an undersanding of how the system mounts storage, work with an api, and further our understanding of linux.
\section{How did you personally approach the problem? Design decisions, algorithm, etc.}
This problem was not very difficult to understand the algorithm as we were just modifying the an existing ramdisk to enable encryption 
\section{How did you ensure your solution was correct? Testing details, for instance.}
We verified that our patch was correct by patching our vm and running it. This process took quite some time as we had to patch it compile it and verify it. 
\section{What did you learn?}
During this project I have learned where some common files are in regards to the kernel. This has opened the doors as to the possibilities to modifying the kernel.

\newpage

\section*{Appendix 1: Source Code}
%\input{__mt19937ar.c.tex}

\end{document}